### 2020-06-29 manuscript/manuscript.rmd
reknit and fix NA in Extended Data Table 1

Historically, there was little debate about the root of the animal tree of life. Porifera-sister (Fig. 1) was widely accepted though rarely tested. By contrast, there has long been uncertainty about the relationship of Ctenophora to other animals [@Wallberg:2004ws]. The first phylogenomic study to include ctenophores [@Dunn:2008ky] suggested a new hypothesis, now referred to as Ctenophora-sister, that ctenophores rather than sponges are our most distant living animal relative. Since then many more relevant phylogenomic studies have been published, with some analyses that find support for Ctenophora-sister, some for Porifera-sister, and some neither (Extended Data Table 1). These studies have taken a wide variety of approaches and results have varied across these different analyses. The extensive technical variation across these studies has been important to advancing the understanding of the sensitivity of these analyses, revealing for example that outgroup and model selection can have a large impact on result. But the larger technical variation has also made it difficult to synthesize these results to understand the details of this sensitivity because so many factors, such as which software tools are used, vary so widely across analyses. This mthodological variance is often confounded, for example when a particular model is only available in one software package.

@@

**Extended Data Table 1.** Table 1. Overview of data matrices used in this study.
```{r table_study_summary}
tableXXdistribution = read_tsv("../data_processed/tables/study_summary.tsv")
  kable(tableXXdistribution)

>>>>

Historically, there was little debate about the root of the animal tree of life. Porifera-sister (Fig. 1) was widely accepted though rarely tested. By contrast, there has long been uncertainty about the relationship of Ctenophora to other animals [@Wallberg:2004ws]. The first phylogenomic study to include ctenophores [@Dunn:2008ky] suggested a new hypothesis, now referred to as Ctenophora-sister, that ctenophores rather than sponges are our most distant living animal relative. Since then many more relevant phylogenomic studies have been published, with some analyses that find support for Ctenophora-sister, some for Porifera-sister, and some neither (Extended Data Table 1). These studies have taken a wide variety of approaches and results have varied across these different analyses. The extensive technical variation across these studies has been important to advancing the understanding of the sensitivity of these analyses, revealing for example that outgroup and model selection can have a large impact on result. But the larger technical variation has also made it difficult to synthesize these results to understand the details of this sensitivity because so many factors, such as which software tools are used, vary so widely across analyses. This methodological variance is often confounded, for example when a particular model is only available in one software package.

@@

**Extended Data Table 1.** Table 1. Overview of data matrices used in this study.
```{r table_study_summary}
table_study_summary = read_tsv("../data_processed/tables/study_summary.tsv")
opts <- options(knitr.kable.NA = "")
knitr::kable(table_study_summary)
